---
title: "The RESTinTown Package Explained"
author: "Nikky Xiong"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RESTinTown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `The RESTinTown` package contains four functions: `cacounty()`, `plot_ca()`, `yelp_api()`, and `RESTinTown()`.

## `cacounty` Function
  
The `cacounty` function joins a few datasets to create a data frame with information of county's name, population in 2010, population in 2019, and land area in California.

```{r eval=FALSE}
library(bestresturantintown)
cacounty()
```

## `plot_ca` Function
  
The `plot_ca` function plots one scatterplot about the population in 2010 and the area of counties in California with the best fitting line for the data frame, ca.

```{r eval=FALSE}
library(bestresturantintown)
plot_ca()
```

## `yelp_api` Function

The `yelp_api` function requests information about Chinese restaurants in one California county on Yelp through Yelp Fusion API. After some analysis, this function returns a data frame with information about the average rating and average review counts for Chinese restaurant in the county, along with the name, rating, and review counts of the best-rated Chinese resturant.

User inputs are required. A `county` needs to be specified to get relative information about Chinese restaurants in this county from Yelp API. A `Yelp_key` is used as the user's key for Yelp API.

```{r eval=FALSE}
library(bestresturantintown)
yelp_api()
```

## `RESTinTown` Function

The `RESTinTown` function relies on `cacounty` and `yelp_api` functions to requests information about Chinese restaurants on Yelp through Yelp Fusion API by each county in California. In the end, this function returns a data frame that contains both information from cacounty and yelp_api, along with new variables of average number of restaurants per person, average number of resturants per square kilometers.

User input is required. A `county` needs to be specified to get relative information about Chinese resturants in this county from Yelp API.

```{r eval=FALSE}
library(bestresturantintown)
RESTinTown()
```
